### 2018-07-23 express2018/unique.tex
Fixed proof of thm 3.10: "exploiting lemma 3.9": maybe explain a bit in a line or so. #7

\begin{definition}
\label{d:uniContra}
Given a  system of contractions 
$\{  X_i \mcontr E_i\}_{i\in I}$, 
 we say that:
\begin{itemize}
\item
 $\til P$ is a \emph{solution  for $\mcontrBIS$ of the 
 system of contractions} 
 if $\til P \mcontrBIS \til E [\til P]$;
\item 
the system  
has  \emph{a unique 
solution for $\approx$}
if 
whenever 
 $\til P$ and $\til Q$ are both solutions  for  $\mcontrBIS$
 then $\til P \approx \til Q$.
\end{itemize}
\end{definition}

\begin{definition}
\label{d:guarded}
A system of contractions $\{  X_i \mcontr E_i\}_{i\in I}$
 is
\emph{weakly guarded}
if,  in each    $E_i$, each occurrence of
a \behavC\ variable is underneath a prefix.

The system use \emph{weakly-guarded sums} if 
each $E_i$ only makes use of guarded sums.
\end{definition}

@@

\begin{proof}{[Sketch]}
Let $n$ be the length of the transition $\ct{\til P}\Arr\mu R$  (the
number of `strong steps' of which it is composed), and  
let $\ctpp {\til P}$ and $\ctpp {\til Q}$  be the processes obtained
from  $\ct {\til P}$ and $\ct {\til Q}$ by unfolding the definitions
of the contractions $n$ times. Thus in $\qctpp$ each hole is
underneath at least $n$ prefixes, and cannot contribute to an action
in the first $n$ transitions; moreover all the contexts use
weakly-guarded sums.

@@

\begin{theorem}[unique solution of contractions for $\wb$]
\label{t:contraBisimulationU}
A system of weakly-guarded contractions
 that uses  weakly-guarded sums    has 
a unique solution 
 for $\wb$.
\end{theorem}

\begin{proof}{[Sketch]}
One shows that if $\til P$ and $\til Q$ are solutions for $\wb$ of a system of weakly-guarded
contractions that uses weakly-guarded sums,  then the
 relation 
\[\R \DSdefi \{ 
(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
$\qct$} \} \, . 
\]
 is a bisimulation, exploiting 
 Lemma~\ref{l:uptocon}.
\end{proof}

@@

\begin{theorem}
\label{t:rcontrPrecongruence}
Relation $\rcontr$ is a precongruence in CCS.  Indeed it is the
largest precongruence contained in $\contr$.
\end{theorem}  
The proof of this result is along the lines of the analogous result
for rooted bisimilarity with respect to bisimilarity. 
%Similarly one can define and handle the rooted variant of the expansion preorder.

For a system of contractions, the meaning of 
``solution for $\rcontr$'' and of 
 \emph{a unique 
solution for $\rapprox$}
is the expected one---just replace in Definition~\ref{d:uniContra}  the preorder 
$\contr$ with $\rcontr$, and the equivalence 
$\approx$ with $\rapprox$.

@@

\begin{theorem}[Unique solution of contractions for $\rapprox$]
\label{t:rcontraBisimulationU}
A system of weakly-guarded contractions
    has 
a unique solution 
 for $\rapprox$.
\end{theorem}

>>>>

\begin{definition}
\label{d:uniContra}
Given a system of contractions 
$\{  X_i \mcontr E_i\}_{i\in I}$, 
 we say that:
\begin{itemize}
\item $\til P$ is a \emph{solution (for $\mcontrBIS$) of the 
 system of contractions} if $\til P \mcontrBIS \til E [\til P]$;
\item the system has \emph{a unique solution (for $\approx$)}
if $\til P \approx \til Q$ whenever $\til P$ and $\til Q$ are both solutions.
\end{itemize}
\end{definition}

The guardedness of contractions follows Def.~\ref{def:guardness} (for equations).
% \begin{definition}
% \label{d:guarded}
% A system of contractions $\{  X_i \mcontr E_i\}_{i\in I}$
%  is
% \emph{weakly guarded}
% if,  in each    $E_i$, each occurrence of
% a \behavC\ variable is underneath a prefix.

% The system use \emph{weakly-guarded sums} if 
% each $E_i$ only makes use of guarded sums.
% \end{definition}

@@

\begin{proof}{(sketch from \cite{sangiorgi2017equations})}
Let $n$ be the length of the transition $\ct{\til P}\Arr\mu R$  (the
number of `strong steps' of which it is composed), and  
let $\ctpp {\til P}$ and $\ctpp {\til Q}$  be the processes obtained
from  $\ct {\til P}$ and $\ct {\til Q}$ by unfolding the definitions
of the contractions $n$ times. Thus in $\qctpp$ each hole is
underneath at least $n$ prefixes, and cannot contribute to an action
in the first $n$ transitions; moreover all the contexts have only
weakly-guarded sums.

@@

\begin{theorem}[unique solution of contractions for $\wb$]
\label{t:contraBisimulationU}
A system of weakly-guarded contractions
having only weakly-guarded sums, has a unique solution for $\wb$.
\end{theorem}

\begin{proof}{(sketch from \cite{sangiorgi2017equations})}
Suppose $\til P$ and $\til Q$ are two such solutions (for $\wb$) and consider
the relation
\begin{equation*}
\R \DSdefi \{ 
(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
$\qct$ (having only weakly-guarded sums)} \} \enspace.
\end{equation*}
We show that $\R$ is a bisimulation. Suppose $R\ \R\ S$ vis the context
$C$, and $R \arr{\mu} R'$. We have to find $S'$ with $S \Arcap{\mu}
S'$ and $R'\ \R\ S'$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
\Arcap{\mu} R'' \wb R'$ for some $R''$. By Lemma~\ref{l:uptocon},
there is $C'$ with $R'' \mcontrBIS C'[{\til P}]$ and $C[{\til Q}]
\Arcap{\mu} \wb C'[{\til Q}]$. Hence, by definition of $\wb$, there is
also $S'$ with $S \Arcap{\mu} S' \wb C'[{\til Q}]$. This closes the
proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$.
\end{proof}

@@

\begin{theorem}
\label{t:rcontrPrecongruence}
$\rcontr$ is a precongruence in CCS, and it is the
coarsest precongruence contained in $\contr$.
\end{theorem}  
The proof of this result is along the lines of the analogous result
for rooted bisimilarity with respect to bisimilarity. 
%Similarly one can define and handle the rooted variant of the
%expansion preorder. (not sure)

For a system of contractions, the meaning of 
``solution for $\rcontr$'' and of 
 \emph{a unique 
solution for $\rapprox$}
is the expected one --- just replace in Definition~\ref{d:uniContra}  the preorder 
$\contr$ with $\rcontr$, and the equivalence 
$\approx$ with $\rapprox$.

@@

\begin{theorem}[unique solution of contractions for $\rapprox$]
\label{t:rcontraBisimulationU}
A system of weakly-guarded contractions has a unique solution 
 for $\rapprox$.
\end{theorem}
